EGGs are adhesive!\\ An algebraic account of equality saturation

### 2025-09-09 jlamp/jlamp.tex
minima

\begin{prop}
Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Let, moreover, $\Gamma_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
\begin{enumerate}
	\item $\lmo_{\mathcal{G}}$ is equivalent to $\comma{M}{\Gamma_\mathcal{G}}$;
	\item $\shyp_{\mathcal{G}}$ is equivalent to $\comma{S}{\Gamma_\mathcal{G}}$; 
	\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp/\sp(\pr(\mathcal{G}))$. 
\end{enumerate}
\end{prop}

@@

\begin{prop}\label{prop:slice}
$\EqHyps$ is equivalent to $\EqHyp/R(\mathcal{G})$.
\end{prop}

@@

Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $E$. By definition and \Cref{lem:pbmono} we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks. Using \Cref{lem:pbmono} and \Cref{lem:epo} we can further deduce that it is stable under pushouts. Then \Cref{thm:slice-functors} and \Cref{cor:eqade} yield the following.

@@

Let $\epbl$ and $\epbs$ be the classes of arrows in  $\elm$, $\eps$ which lies, respectively in $\pbl$ and $\pbs$. By Lemmas \ref{lem:equ}, \ref{lem:coequ} and \Cref{cor:pbe} we obtain immediately the following result.

\begin{cor}
	$\elm$ is $\epbl$-adhesive, while $\eps$ is $\epbs$-adhesive.
\end{cor}

>>>>

\begin{prop}
Let $M\colon \lmo \to \hyp$ and $S\colon \shyp \to \hyp$ be the inclusion functors. Moreover, let $\Gamma_{\mathcal{G}}\colon 1\to \hyp$ be the constant functor in $\mathcal{G}$. Then
\begin{enumerate}
	\item $\lmo_{\mathcal{G}}$ is equivalent to $\comma{M}{\Gamma_\mathcal{G}}$;
	\item $\shyp_{\mathcal{G}}$ is equivalent to $\comma{S}{\Gamma_\mathcal{G}}$; 
	\item $\pshyp_{\mathcal{G}}$ is equivalent to $\pshyp/\sp(\pr(\mathcal{G}))$. 
\end{enumerate}
\end{prop}

@@

\begin{prop}\label{prop:slice}
$\EqHyps$ is equivalent to $\EqHyp \downarrow R(\mathcal{G})$.
\end{prop}

@@

Let now $\pbe$ be the class of arrows in $\egg$ that are sent to $\pbc$ by $E$. By definition and \Cref{lem:pbmono}, we have that such class is closed under composition and decomposition, it contains all isomorphisms and it is stable under pullbacks. Using \Cref{lem:pbmono} and \Cref{lem:epo} we can further deduce that it is stable under pushouts. Then \Cref{thm:slice-functors} and \Cref{cor:eqade} yield the following.

@@

Let $\epbl$ and $\epbs$ be the classes of arrows in  $\elm$ and $\eps$ lying in $\pbl$ and $\pbs$, respectively. By Lemmas \ref{lem:equ}, \ref{lem:coequ} and \Cref{cor:pbe} we obtain immediately the following result.

\begin{cor}
	$\elm$ is $\epbl$-adhesive and $\eps$ is $\epbs$-adhesive.
\end{cor}
